### 2016-01-07 p2/def-commands.tex
Minor improvements

We use $\cchard$, $\ccharf$ or $\ccharb$ to represent the different
types, and omit the final value if it is determined by the output type
(when it is $\empt$ or $\vald$).
For example, $\cbdaa{n}{\vald}$ will represent $mkdir(n,\vald)$,
and $\cdba{n}$ will represent $rmdir(n)$.
\end{mydef}

@@

To define the exact effect of the commands we use
the \emph{replacement operator}  which changes the
value of the filesystem at a given point only.

>>>>

We use $\cchard$, $\ccharf$ or $\ccharb$ to represent the different
types, and omit the final value if it is determined by the output type
(when it is $\empt$ or $\vald$).
For example, $\cbfaa{n}{\valf}$ will represent $create(n,\valf)$,
and $\cdba{n}$ will represent $rmdir(n)$.
\end{mydef}

@@

To define the exact effect of the commands we use
the \emph{replacement operator}  which changes the
value of the filesystem at a given node only.

### 2016-01-07 p2/def-filesystem.tex
Minor improvements

The nodes form a disjoint union of rooted directed trees,
which determines the following $\parent$ function,
and \emph{ancestor / descendant} and \emph{incomparable} relations.
Tao et al. in \cite{TSR} describe a similar filesystem model, although
they also model inodes and restrict the filesystem to a just single tree.
\begin{mydef}[$\parent$]
The function $\parent(n)$ returns the parent node of $n$, or
returns $\topnode$ if $n$ is the root of a tree.
\end{mydef}

>>>>

The nodes form a disjoint union of rooted directed trees,
which determines the following $\parent$ function,
and the \emph{ancestor / descendant} and \emph{incomparable} relations.
Tao et al. \cite{TSR} describe a similar filesystem model, although
they also model inodes and restrict the filesystem to a just single tree.
\begin{mydef}[$\parent$]
The function $\parent(n)$ returns the parent node of $n$, or
returns $\topnode$ if $n$ is the root of a tree.
\end{mydef}
